%
% Modified by Sameer Vijay
% Last Change: Wed Jul 27 2005 13:00 CEST
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Sample Notre Dame Thesis/Dissertation
% Using Donald Peterson's ndthesis classfile
%
% Written by Jeff Squyres and Don Peterson
%
% Provided by the Information Technology Committee of
%   the Graduate Student Union
%   http://www.gsu.nd.edu/
%
% Nothing in this document is serious except the format.  :-)
%
% If you have any suggestions, comments, questions, please send e-mail
% to: ndthesis@gsu.nd.edu
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%
% Chapter 2
%

\chapter{TRANSFER REACTIONS AND NUCLEAR MATRIX ELEMENTS}
\label{chap:nucl}

\section{Shell Model of the Nucleus}
\begin{comment}
Using H.O. eigenstates to describe nucleons.
\begin{itemize}
\item nuclear potential well - is this something we can understand independently?  Certainly the radius is.
\item solutions to finite square well in terms of H.O. eigenstates and a diagram of energy levels
\item the energy levels give correct shell closures when spin-orbit coupling is introduced
\item so H.O. eigenstates are a reasonable way to describe nucleons
\end{itemize}

Looking at the valence nucleons to understand the whole nucleus.
\begin{itemize}
\item and because the nucleons couple so strongly into \zp pairs, describing the unpaired nucleons often accurately describes the entire nucleus
\item give a simple example?  \He{3} might be useful?
\item show level filling for \Ge{74} (32 protons) and point out the valence nucleons are f, p, g
\end{itemize}
\end{comment}

In this work, HO eigenstates will be used exclusively as the basis set when describing nuclear wavefunctions.  Trends in systematic nuclear data such as nuclear mass gave clear evidence of ``magic numbers'' of protons and neutrons in nuclei, but it was not until Maria Goeppert-Mayer added a spin-orbit term to the HO potential that these magic numbers were correctly reproduced.  Describing a nucleus with more than three nucleons in any basis set would be an arduous task were it not for the surprisingly accurate assumption that closed shells in the nucleus form an inert core with $J=0$.  Furthermore, nucleons have a strong tendency to couple into $J=0$ pairs, so that to understand the behavior of the nucleus it is often sufficient to understand only the behavior of the unpaired nucleons.

The nuclei of interest in this work, \GeTargets, have 32 protons and 32 and 34 neutrons, respectively.  Like all even-even nuclei, their ground states are \zp, evidencing the strong coupling of nucleons into $J=0$ pairs.  The nucleons studied by ($^3$He,n) transfer are proton-pair holes; the valence shell of \GeTargets are shown in {\fig}~\ref{fig:valence}.  It is important to note that while the central potential with spin-orbit coupling accurately reproduces the magic numbers seen in nuclear data, it is by no means a universal potential that accurately describes all nuclei.  The exact energy levels in \GeTargets are not known, and so the valence shell is considered to be f-p-g rather than simply 1f$_{5/2}$.

\section{Nucleon States and the Impact they Have on NME}
\subsection{NME calculations and valence States}
\begin{itemize}
\item (assume that) NME calculations are sensitive to occupied valence states
\item can investigate valence state occupation with transfer reactions
\item \Ge{76} occupancies were experimentally determined and adjusting the energy levels to match changed the NME by a factor of 2 \cite{0vbbReview}
\end{itemize}


\section{Nucleon-nucleon correlations and the impact they have on NME}
\begin{itemize}
\item \zvbb occurs on correlated neutron pairs
\item certain pairing in the nucleus can inhibit \zvbb
\item investigate pair correlation with two-nucleon transfer reactions
\item some systems don't have all their \zp in the ground state - Xe
\item discuss neutron transfer experiments done on \GeTargets
\item wish to investigate proton transfer on \GeTargets
\end{itemize}


\section{Modeling two-proton Transfers}
Discuss DWBA theory of two-proton transfer reactions
\begin{equation}
M\sim\langle\psi_n|V_T|\psi_{^3He}\rangle
\end{equation}
Where $V_T$ is the transfer operator and $\psi$ are elastic scattering wave functions.
Assume that nuclear elastic scattering is the largest contribution to the nuclear reaction and use 1st order perturbation theory to generate $V_T$ from the bound-state wave functions.
To get $\psi$ (?)
\begin{enumerate}
\item treat two particles individually
\item treat two protons as bound cluster
\end{enumerate}
treating particles individually is too complicated
when using cluster model, can adjust $V_0$ of well to match ?? binding energy and adjust $r_0$ to adjust range and $a_0$ to adjust ??.

cluster model's prediction of 0 degree cross section is sensitive to these parameters, but the relative cross sections of f-p-g shell nuclei do not depend strongly on the parameters.

Discuss experimental difficulties of two-proton transfer reactions and introduce NSL as a good place to do them

% % uncomment the following lines,
% if using chapter-wise bibliography
%
% \bibliographystyle{ndnatbib}
% \bibliography{example}
