%
% Modified version of the sample_ndthesis.tex
% by Sameer Vijay
% Last Change: Wed Jul 27 2005 14:00 CEST
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Sample Notre Dame Thesis/Dissertation
% Using Donald Peterson's ndthesis classfile
%
% Written by Jeff Squyres and Don Peterson
%
% Provided by the Information Technology Committee of
%   the Graduate Student Union
%   http://www.gsu.nd.edu/
%
% Nothing in this document is serious except the format.  :-)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This is *not* a substitute for Donald's orginial documentation.  See
% /afs/nd.edu/usr/local/src/tex/texmf/doc/latex/ndthesis/ndthesis.dvi
% for documentation on the particular commands and whatnot.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% You should *also* have a ND formatting guide to ensure that you have
% all the relevant parts, put the captions in the right place, etc.
% Just because you have this wonderful style classfile doesn't mean
% that it removes *all* the formatting onus from you.  :-)
%
% Normally, you should break all of this stuff up into separate files
% (at the very least, one chapter per file) and use the \input
% command.  This is all one file for brevity's (and clarity's) sake.
%
% Note that you should also have a good Makefile; one that invokes
% LaTeX as many times as necessary (up to 4) and bibtex if necessary.
% One should be included in this distribution.  You may want to modify
% the Makefile to make separate chapters, if necessary.
%
% If you have any suggestions, comments, questions, please send e-mail
% to: ndthesis@gsu.nd.edu
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\documentclass[textrefs,review]{nddiss2e}
\documentclass[textrefs,final,noinfo,12pt]{nddiss2e}

\usepackage[lofdepth,lotdepth]{subfig}
\usepackage{floatrow}
%\usepackage{epsfig}
\usepackage{graphicx}
%\usepackage{epstopdf}
%\usepackage[pdf]{pstricks}
%\usepackage{adjustbox}
\usepackage{booktabs}
\usepackage{xspace}
\usepackage{comment}
\usepackage{amsmath}
\usepackage{caption}
\usepackage{rotating}

\newcommand{\ra}[1]{\renewcommand{\arraystretch}{#1}}
\newcommand{\fig}{Figure\xspace}
\newcommand{\tab}{Table\xspace}
\newcommand{\sect}{Section\xspace}
\newcommand{\chap}{Chapter\xspace}
\newcommand{\eqn}{Equation\xspace}
\newcommand{\app}{Appendix\xspace}
\newcommand{\Ge}[1]{$^{#1}$Ge\xspace}
\newcommand{\As}[1]{$^{#1}$As\xspace}
\newcommand{\Se}[1]{$^{#1}$Se\xspace}
\newcommand{\Mg}[1]{$^{#1}$Mg\xspace}
\newcommand{\Si}[1]{$^{#1}$Si\xspace}
\newcommand{\He}[1]{$^{#1}$He\xspace}
\newcommand{\GeTargets}{$^{74,76}$Ge\xspace}
\newcommand{\SeProducts}{$^{76,78}$Se\xspace}
\newcommand{\reaction}{$^{74,76}$Ge($^3$He,n)$^{76,78}$Se\xspace}
\newcommand{\MgReaction}{$^{26}$Mg($^3$He,n)$^{28}$Si\xspace}
\newcommand{\DuReaction}{d(d,n)$^3$He\xspace}
\newcommand{\zvbb}{$0\nu\beta\beta$\xspace}
\newcommand{\tvbb}{$2\nu\beta\beta$\xspace}
\newcommand{\NME}{$M^{0\nu}$\xspace}
\newcommand{\zp}{$0^+$\xspace}
\newcommand{\tp}{$2^+$\xspace}
\bibpunct{[}{]}{,}{n}{}{;}
% % uncomment the following line 
% if using chapter-wise bibliography
% \usepackage{chapterbib}
% \renewcommand{\bibname}{Cited Works}
% \renewcommand{\bibsection}{\section{\bibname}}

\begin{document}

\frontmatter

\title{TWO-PROTON TRANSFER ONTO GE \\ {\small\scshape HELPING OUT THE NEUTRINO PEOPLE} }
\author{Amy Roberts}
\work{Dissertation}
\degprior{B.S.}
\degaward{Doctor of Philosophy\\in\\Physics}
\advisor{James Kolata}
% \secondadvisor{Gordon Gray}
\department{Physics}

\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Front stuff
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\copyrightholder{Amy Roberts}
\copyrightyear{2013}
\makecopyright

\begin{abstract}
A great deal of effort has gone into detecting neutrinoless double beta decay (\zvbb).  But the nuclei that offer the greatest chance of observing this phenomenon are poorly understood.  While an observation of \zvbb has dramatic implications all by itself, there are compelling reasons to better understand the nuclei that might play host to such an event.  The nucleus affects the rate of such an event, important in planning experiments.  And should \zvbb be detected, the nucleus must be well-understood to extract parameters such as the absolute mass scale of the neutrino.

For many years, the nuclear community has worked to piece together a clearer understanding of these nuclei using single-nucleon transfer reactions.  Two-nucleon transfer reactions are also of fundamental importance.  This work investigates two-proton transfer onto \Ge{76} and \Ge{78}.
\end{abstract}

\renewcommand{\dedicationname}{New Dedication Name}

\begin{dedication}
  To George, my favorite Gnu
\end{dedication}

\tableofcontents
\listoffigures
\listoftables

\begin{preface}
  Nuclear physics has been working had for decades to better understand the Nuclear Matrix Elements (NME) of nuclei used in \zvbb studies.  The field has made significant strides; where first it was thought that data from neutrino-full double beta decay provided sufficient information, subsequent theory work showed that this was not the case.  Since then, exhaustive assays of single-nucleon transfers have contributed significantly to the understanding of nucleon occupancy (spoiler alert - it's more complicated than we'd like), and with the guidance of theorists, have begun exploring two-nucleon transfer reactions to better understand correlations between nucleons within these nuclei.  This experiment is the final two-nucleon transfer reaction for the Ge isotope.

  What this thesis will do is present the data from the transfer reaction.  What this thesis will not do is explain how this affects \zvbb.
\end{preface}

\begin{acknowledge}
  I would like to thank the Notre Dame community, particularly the physics department and health services, who kept me well and worked hard to teach me some physics.  I would also like to thank my advisor, Dr.\ James Kolata, without
  whom this work would not have been possible.

  Finally, I would like to thank the U.S.\ Government, Department of
  Gnus, for their generous grant, number GNU3042920920.3, which
  allowed me to pursue my work.
\end{acknowledge}

\begin{symbols}
  \sym{\mathcal{F}}{sighting frequency of Gnus about campus}
  \sym{p}{student population}
  \sym{f}{type of food available}
  \sym{d}{day of week}
  \sym{c}{speed of light}
  \sym{m}{mass}
  \sym{e}{elementary charge}
  \sym{a,b}{miscellaneous constants}  
  \sym{E}{energy}  
\end{symbols}

\mainmatter
\setcounter{chapter}{0}
%
% Chapter 1
%

\include{chapter1}


%
% Chapter 2
%

\include{chapter2}


%
% Chapter 3
%

\include{chapter3}



%
% Chapter 4
%

\include{chapter4}



%
% Chapter 5
%

\include{chapter5}



%
% Chapter 6
%

\include{conclude}



%
% Appendix
%

\appendix

\include{appendix}


%
% Back stuff
%

% % comment out the following three lines
% if using chapter-wise bibliography

 \backmatter
 \bibliographystyle{nddiss2e}
 \bibliography{thesis}

\end{document}

% End of ``example.tex''
